Put Title here

### 2018-12-18 General WLD combinatorics.tex
updated the notation in the proof of the number of plusses

Agarwala and Marcott show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$. Their proof is geometric and elegant, but it is not easy to track the effect of a particular propagator.

@@

\note{Karen got to here, but there are no other uses of Lemma~\ref{lem sian}, so the rest just needs notational/style updates (unless we find problems)}

\begin{lem}\label{lem I}
  Let $D$ be a WLD with $n\geq 1$ propagators and let $p$ be a propagator of $D$ so that the properties of Lemma~\ref{lem good p} are satisfied for $p$ in $D$ (that is $D$ is already appropriately transformed).  Furthermore suppose that that $p$ has length $2$, as does $q$ if we are in the case of Lemma~\ref{lem good p} involving $q$.  Let $C$ be $D$ with $p$ removed but no change in the vertices.  Then
  \begin{align*}
    I_1^{D} & = I_1^{C} \cup \{n-3\} \\
    I_n^{D} & = I_1^{C} \cup \{n\} \\
    I_{n-1}^{D} & = I_n^{C} \cup \{n-1\} \\
    I_{n-2}^{D} & =
    \begin{cases}
      I_{n-2}^{C}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{C}$} \\
      I_{n-2}^{C}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{C}$, $n-1\not\in I_{n-2}^{C}$} \\
      (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{C}$}
    \end{cases} \\
    I_{k}^{D} & =
    \begin{cases}
      I_k^{C}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{C}$}\\
      I_k^{C}\cup\{n-2\} & \text{if $n-3\in I_k^{C}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

\begin{figure}
 \includegraphics{specialp}
  \caption{The different possibilities for $D$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
\end{figure}

@@

  If $n-3\in I_1^{C}$ then $n-3\not\in I_1^{D}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{vertex cyclic int lem}.  Thus $n-3\not\in I_1^{C}$ and so in building the Gra\ss mann necklace when we get to vertex $n-3$ any other covering propagators of $C$ have already been taken and so we can now take $p$.  Therefore $I_1^{D}= I_1^{C}\cup \{n-3\}$.

  In constructing $I_n^{D}$, first for vertex $n$ we take propagator $p$.  Then we are at vertex $1$ and precisely the propagators of $C$ remain.  Thus the rest of the construction will give $I_1^{C}$.  Therefore $I_n^{D} = I_1^{C}\cup \{n\}$.  Essentially the same reasoning gives $I_{n-1}^{D} = I_n^{C}\cup \{n-1\}$.

  Now consider $I_{n-2}^{D}$.  If $n-2\not\in I_{n-2}^{C}$ then at vertex $n-2$ we take $p$ and this does not affect the rest of the construction of $I_{n-2}^{C}$, so $I_{n-2}^{D} = I_{n-2}^{C}\cup \{n-2\}$.  An analogous argument takes care of the first case for $I_k^{D}$.  Suppose $n-2\in I_{n-2}^{C}$ but $n-1\not\in I_{n-2}^{C}$.  Then at vertex $n-2$ we take the same propagator in $C$ as in $D$ (in particular not $p$) because $p$ is the counterclockwisemost propagator covering $n-2$ and so the last propagator the algorithm would choose at this vertex, and by hypothesis $n-2$ is covered in $C$.  Howver, $n-1$ is untaken in $I_{n-2}^{C}$ so at this vertex we will take $p$ in $I_{n-2}^{D}$.  Following this, now that $p$ is out of the way without bumping any other propagators, the construction continues as in $I_{n-2}^{C}$.  Therefore $I_{n-2}^{D} = I_{n-2}^{C}\cup \{n-1\}$.  An analogous argument takes care of the case when we have $1<k<n-2$ and $n-3\in I_k^{C}$ but $n-2\not\in I_{k}^{C}$.  Furthermore, either $n-2$ is uncovered in $C$ or only $q$ covers $n-2$ in $C$ and $q$ is also the only propagator covering $n-3$.  Thus it is not possible for $n-3$ and $n-2$ to both be in $I_{k}^{C}$.  This means that all the cases for $I_k^{D}$ are now proved.

  The remaining case is when $n-1,n-2\in I_{n-2}^{C}$ for the construction of $I_{n-2}^{D}$.  We must then have a propagator $q$ as in the right hand side of Figure~\ref{fig special p}.  In the construction of $I_{n-2}^{D}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{C}$.  Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{C}$.  Next we are at vertex $n$ and propagators $p$ and $q$ have been taken.  Thus we are proceeding like $I_{n}^{C}$ but without propagator $q$.  Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{C}$.  By Lemma~\ref{vertex cyclic int lem} propagator $q$ contributes $n-5$ to $I_{n}^{C}$, and the only way this can occur is if all other propagators of $C$ were already taken by the time we got to vertex $n-5$.  Therefore $I_{n-2}^{D} = (I_{n}^{C} - \{n-5\}) \cup \{n-1, n-2\}$.  This covers all cases and hence completes the proof.
\end{proof}

\subsubsection{The number of plusses from Gra\ss mann necklaces in nice configurations}

\begin{lem}\label{lem shape}
  Let $C$ and $D$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $C$ can be built from left to right of the following blocks: a rectangle with 3 columns, one more column of the same length, a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $D$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $C$, the same partition shape as in $C$.
\end{lem}

\begin{proof}
  $I_1$ determines the shape of the Le diagram.
  By Lemma~\ref{lem I}, $I_1^{D} = I_1^{C}\cup \{n-3\}$.  This implies that the right hand boundary of the shape of $C$ is the same as the right hand boundary of the shape of $D$ except that $D$ has one additional row of 3 boxes while $C$ has an additional column in the $n-3$ position, that is a new column fourth from the left.
\end{proof}

The shapes of the Le diagrams of $C$ and $D$ are illustrated in Figure~\ref{fig Le}.  The pieces of the Le diagrams will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows, as in the figure.  Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of the Le diagrams of $C$ and $D$ are identical and the plusses in the $\mathcal{A}$ parts are very closely related.  When we speak of a plus in the Le diagram of $D$ being the same as in $D$ or vice versa, we mean that the plus' position in $\mathcal{A}$ or $\mathcal{B}$ is the same.  Because of the column insertion the absolute indices may differ.

\begin{figure}
  \includegraphics{Le_diagrams}
  \caption{Le diagrams for $C$ (left) and $D$ (right).}\label{fig Le}
\end{figure}

Suppose we are following the Gra\ss mann necklace to Le diagram algorithm, and we put a plus in a box because of a path from vertical boundary edge $i$ to bottom boundary edge $j$.  Then say this plus is in the $i\rightarrow j$ position.

\begin{lem}\label{lem n and n-1}
  Let $C$ and $D$ be as in Lemma~\ref{lem I}.
  The $I_n^{D}$ and $I_{n-1}^{D}$ elements of the Gra\ss mann necklace of $D$ give all the same plusses as $I_n^{C}$ along with plusses in the leftmost two boxes of the bottom row of the Le diagram of $D$.
\end{lem}

\begin{proof}
  By Lemma~\ref{lem I} $I_n^{D}= I_1^{C} \cup \{n\}$, so by the Gra\ss mann necklace to Le diagram algorithm the only plus this builds in the Le diagram of $D$ is  the one in the $n-3\rightarrow n$ position, that is in the leftmost box of the bottom row.

  Also by Lemma~\ref{lem I} $I_{n-1}^{D} = I_n^{C} \cup \{n-1\}$.  Additionally $n-3\not\in I_{n}^{C}$ since if it were then $n-3$ would also be in $I_1^{C}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{D}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.  Similarly $n-1, n-2\not\in I_n^{C}$.  Thus the paths putting the plusses in from $I_n^{C}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $D$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{D}$ contributes.  That is, we get all the plusses from $I_{n}^{C}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
\end{proof}

\begin{lem}\label{lem n-2 good}
  Let $C$ and $D$ be as in Lemma~\ref{lem I} with $n-2 \not\in I_{n-2}^{C}$.

  The $I_{n-2}^{D}$ element of the Gra\ss mann necklace of $D$ gives
  an $n-3\rightarrow n-2$ plus and
  all the $I_{n-1}^{C}=I_{n-2}^{C}$ plusses.
\end{lem}

\begin{proof}
  If $n-2\not\in I_{n-2}^{C}$ then $I_{n-1}^{C}=I_{n-2}^{C}$ and by Lemma~\ref{lem I} $I_{n-2}^{D} = I_{n-1}^{C} \cup \{n-2\}$.  Note that $n-3\not\in I_{n-2}^{C}$ by Lemma~\ref{vertex cyclic int lem}.  Therefore the paths for $I_{n-2}^{D}$ are the paths for $I_{n-1}^{C}$ along with the $n-3\rightarrow n-2$ path.  This gives the statement of the lemma.

@@

\begin{lem}\label{lem n-2 bad}
  Let $C$ and $D$ be as in Lemma~\ref{lem I} with $n-2,n-1 \in I_{n-2}^{C}$.

  The $I_{n-2}^{D}$ and $I_{n-3}^{D}$ elements of the Gra\ss mann necklace of $D$ gives the following plusses:
  \begin{itemize}
  \item An $n-3\rightarrow n-2$ plus and an $n-5\rightarrow n-1$ plus.
  \item All the $I_{n-1}^{C}$ plusses.
  \item $I_{n-2}^{C}$ gives an $n-5\rightarrow n-2$ plus and no other term in the Gra\ss mann necklace of $C$ gives a plus in this column.  This $+$ does not appear in $D$ from $I_{n-2}^{D}$ but an $n-5\rightarrow n-1$ plus does instead.
  \item All other plusses of $I_{n-2}^{C}$.
  \item $I_{n-3}^{C}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $D$.
  \item All other plusses of $I_{n-3}^{C}$.
  \end{itemize}
  Furthermore, no element of the Gra\ss mann necklace of $C$ gives an $n-5\rightarrow n-1$ plus.
\end{lem}

\begin{proof}
  By Lemma~\ref{lem I} $I_{n-2}^{D}= (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\}$.  Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{C}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.  Thus this section of the Gra\ss mann necklace of $C$ looks like
  \begin{equation}\label{eq necklace}
  I_{n-3}^{C} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{C} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{C} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{C} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{C}
  \end{equation}
  where the first ``something'' is either $n$ or an element of $I_1^{C}$ and the second ``something'' is an element of $I_1^{C}$.  Additionally all elements not explicitly mentioned must be in $I_1^{C}$ as they remain unchanged through this portion of the necklace.

  Using this information now determine the symmetric difference of $I_{n-2}^{C}$ and $I_1^{C}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{C}$ but not in $I_1^{C}$.  $n-5$ is in $I_1^{C}$ as are at least one and at most two other elements.  If there is one such element call it $a$.  If there are two call them $a$ and $b$ with $a>b$.  This means that the plusses in the Le diagram of $C$ coming from $I_{n-2}^{C}$ are as in the first part of Figure~\ref{fig messy}.  Stepping to $I_{n-1}^{C}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.

  \begin{figure}
    \includegraphics{messy}
    \caption{Plusses coming from $I_{n-2}^{C}$ (top left),  $I_{n-1}^{C}$ (top right) and $I_{n}^{C}$ bottom when $n-1, n-2\in I_{n-1}^{C}$.  The blue lines are the non-intersecting paths.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure}

  Stepping to $I_{n}^{C}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.  This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.

  Now we know that $I_{n-2}^{D}  = (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{D}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{C}$ to $\{n-2, n-1, n\}$.  This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}

  \begin{figure}
     \includegraphics{messyD}
    \caption{Plusses coming from $I_{n-2}^{D}$.}\label{fig messyD}
  \end{figure}

@@

  Now consider $I_{n-3}^{C}$.  By \eqref{eq necklace} $I_{n-3}^{C}$ contributes the same plusses as $I_{n_2}^{C}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.  Also, we have $n-3\in I_{n-3}^{C}$ be the location of $q$ and so $I_{k}^{D} = I_k^{C}\cup\{n-2\}$.  Thus the paths for $I^{D}_{n-3}$ are the same as for $I^{C}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.  This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{C}$ among the necklace elements of $C$.

  Also note that $I_{n-3}^{C}, I_{n-2}^{C}$, and $I_{n-1}^{C}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.

  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $C$.  By the algorithm, it would have to come when $n-5 \not\in I_j^{C}$.  By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{C}$, $I_{n-3}^{C}$, or $I_{n-2}^{C}$. The analysis above shows it does not come from $I_{n-3}^{C}$ or $I_{n-2}^{C}$.   Now, $n-4\in I_{n-4}^{C}$ by the location of $q$ and so $I_{n-4}^{C}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.

@@

\begin{lem}\label{lem other k}
  Let $C$ and $D$ be as in Lemma~\ref{lem I} and take $1<k<n-2$.  Suppose that if $n-2\in I_{n-2}^{C}$ then also $n-1\in I_{n-2}^{C}$.
  The $I_k^{D}$ element of the Gra\ss mann necklace of $D$ gives the same plusses as $I_{k}^{C}$ except that if there is a plus in the $n-3$ column for $I_{k}^{C}$ then this plus is shifted into the $n-2$ column and no plus was already in that location.
\end{lem}

\begin{proof}
  If $n-3\not\in I_{k}^{C}$ then by Lemma~\ref{lem I} $I_{k}^{D} = I_k^{C}\cup \{n-3\}$.  Then since $n-3$ is the largest element of $I_1^{D}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $C$ to $D$ directly.

  If $n-3\in I_{k}^{C}$ then by Lemma~\ref{lem I} $I_{k}^{D} = I_k^{C}\cup \{n-2\}$.  If $n-2$ is not covered in $C$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $C$.  If $n-2$ is covered in $C$ then by hypothesis so is $n-1$ and so we satisfy the hypotheses of Lemma~\ref{lem n-2 bad}.  Thus the only necklace element of $C$ containing $n-2$ is $I_{n-2}^{C}$ and this particular plus is not contributed to the Le diagram of $D$ by $I_{n-2}^{D}$.

  {}From $I_{k}^{C}$ there is a path from some vertical edge to the bottom edge $n-3$.  In $I_{k}^{D}$, $n-3$ is a vertical edge with no path and instead there must be a path to $n-2$.  By the previous paragraph no other path can end in $n-2$, so shifting the path that did go to $n-3$ to go to $n-2$ while leaving the others the same maintains non-crossingness and so must be the paths for $I_{k}^{D}$.  Thus the plus in the $n-3$ column for $C$ is shifted into the $n-2$ column, where there was no plus before, and no other plusses are changed.
\end{proof}

>>>>

Agarwala and Marcott show ***cite this*** that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$. Their proof is geometric and elegant, but it is not easy to track the effect of a particular propagator.

@@

\begin{lem}\label{lem I}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Suppose $p$ is a propagator of $W$ so that the properties of Lemma~\ref{lem good p} are satisfied for $p$ in $W$ and that $p$ has length $2$, as does $q$ if we are in the case of Lemma~\ref{lem good p} involving $q$.  Let $V$ be $W$ with $p$ removed.  Then
  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

\begin{figure}
 \includegraphics{specialp}
  \caption{The different possibilities for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
\end{figure}

@@

  If $n-3\in I_1^{V}$ then $n-3\not\in I_1^{W}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{vertex cyclic int lem}.  Thus $n-3\not\in I_1^{V}$ and so in building the Grassmann necklace when we get to vertex $n-3$ any other propagators of $V$ which are supported at $n-3$ have already been taken and so we take $p$.  Therefore $I_1^{W}= I_1^{V}\cup \{n-3\}$.

  In constructing $I_n^{W}$, first for vertex $n$ we take propagator $p$.  Then we are at vertex $1$ and precisely the propagators of $V$ remain.  Thus the rest of the construction will give $I_1^{V}$.  Therefore $I_n^{W} = I_1^{V}\cup \{n\}$.  Essentially the same reasoning gives $I_{n-1}^{W} = I_n^{V}\cup \{n-1\}$.

  Now consider $I_{n-2}^{W}$.  If $n-2\not\in I_{n-2}^{V}$ then at vertex $n-2$ we take $p$ and this does not affect the rest of the construction of $I_{n-2}^{V}$, so $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$.  An analogous argument takes care of the first case for $I_k^{W}$.  Suppose $n-2\in I_{n-2}^{V}$ but $n-1\not\in I_{n-2}^{V}$.  Then at vertex $n-2$ we take the same propagator in $V$ as in $W$ (in particular not $p$) because $p$ is the counterclockwisemost propagator supported on $n-2$ and so the last propagator the algorithm would choose at this vertex, and by hypothesis $n-2$ does support at least one propagator in $V$.  However, $n-1$ is not yet taken in $I_{n-2}^{V}$, so at this vertex we will take $p$ in $I_{n-2}^{W}$.  Following this the construction continues as in $I_{n-2}^{V}$.  Therefore $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$.  An analogous argument takes care of the case when we have $1<k<n-2$ and $n-3\in I_k^{V}$ but $n-2\not\in I_{k}^{V}$.  Furthermore, either $n-2$ supports no propagators in $V$ or only $q$ is supported by $n-2$ in $V$ and $q$ is also the only propagator supported by $n-3$.  Thus it is not possible for $n-3$ and $n-2$ to both be in $I_{k}^{V}$.  This means that all the cases for $I_k^{W}$ are now proved.

  The remaining case is when $n-1,n-2\in I_{n-2}^{V}$ for the construction of $I_{n-2}^{W}$.  We must then have a propagator $q$ as in the right hand side of Figure~\ref{fig special p}.  In the construction of $I_{n-2}^{W}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{V}$.  Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{V}$.  Next we are at vertex $n$ and propagators $p$ and $q$ have been taken.  Thus we are proceeding like $I_{n}^{V}$ but without propagator $q$.  Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{V}$.  By Lemma~\ref{vertex cyclic int lem} propagator $q$ contributes $n-5$ to $I_{n}^{V}$, and the only way this can occur is if all other propagators of $V$ were already taken by the time we got to vertex $n-5$.  Therefore $I_{n-2}^{W} = (I_{n}^{V} - \{n-5\}) \cup \{n-1, n-2\}$.  This covers all cases and hence completes the proof.
\end{proof}

\begin{lem}\label{lem shape}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle with 3 columns, one more column of the same length, a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, the same partition shape as in $V$.
\end{lem}

\begin{proof}
  $I_1$ determines the shape of the Le diagram.
  By Lemma~\ref{lem I}, $I_1^{W} = I_1^{V}\cup \{n-3\}$.  This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, a new column fourth from the left.
\end{proof}

The shapes of the Le diagrams of $V$ and $W$ are illustrated in Figure~\ref{fig Le}.  The pieces of the Le diagrams will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows, as in the figure.  Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of the Le diagrams of $V$ and $W$ are identical and the plusses in the $\mathcal{A}$ parts are very closely related.  When we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the plus' position in $\mathcal{A}$ or $\mathcal{B}$ is the same.  Because of the column insertion the absolute indices may differ.

\begin{figure}
  \includegraphics{Le_diagrams}
  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
\end{figure}

Suppose we are following the Grassmann necklace to Le diagram algorithm, and we put a plus in a box because of a path from vertical boundary edge $i$ to bottom boundary edge $j$.  Then say this plus is in the $i\rightarrow j$ position.

\begin{lem}\label{lem n and n-1}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  Then $I_n^{W}$ and $I_{n-1}^{W}$ give all the same plusses as $I_n^{V}$ along with plusses in the leftmost two boxes of the bottom row of the Le diagram of $W$.
\end{lem}

\begin{proof}
  By Lemma~\ref{lem I} $I_n^{W}= I_1^{V} \cup \{n\}$, so by the Grassmann necklace to Le diagram algorithm the only plus this builds in the Le diagram of $W$ is  the one in the $n-3\rightarrow n$ position, that is in the leftmost box of the bottom row.

  Also by Lemma~\ref{lem I} $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.  Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.  Similarly $n-1, n-2\not\in I_n^{V}$.  Thus the paths putting the plusses in from $I_n^{V}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $W$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{W}$ contributes.  That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
\end{proof}

\begin{lem}\label{lem n-2 good}
  Let $V$ and $W$ be as in Lemma~\ref{lem I} with $n-2 \not\in I_{n-2}^{V}$.

  Then $I_{n-2}^{W}$ gives
  an $n-3\rightarrow n-2$ plus and
  all the $I_{n-1}^{V}=I_{n-2}^{V}$ plusses.
\end{lem}

\begin{proof}
  If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ and by Lemma~\ref{lem I} $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.  Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{vertex cyclic int lem}.  Therefore the paths for $I_{n-2}^{W}$ are the paths for $I_{n-1}^{V}$ along with the $n-3\rightarrow n-2$ path.  This gives the statement of the lemma.

@@

\begin{lem}\label{lem n-2 bad}
  Let $V$ and $W$ be as in Lemma~\ref{lem I} with $n-2,n-1 \in I_{n-2}^{V}$.

  Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ give the following plusses:
  \begin{itemize}
  \item An $n-3\rightarrow n-2$ plus and an $n-5\rightarrow n-1$ plus.
  \item All the $I_{n-1}^{V}$ plusses.
  \item $I_{n-2}^{V}$ gives an $n-5\rightarrow n-2$ plus and no other term in the Gramann necklace of $V$ gives a plus in this column.  This $+$ does not appear in $W$ from $I_{n-2}^{W}$ but an $n-5\rightarrow n-1$ plus does instead.
  \item All other plusses of $I_{n-2}^{V}$.
  \item $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
  \item All other plusses of $I_{n-3}^{V}$.
  \end{itemize}
  Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
\end{lem}

\begin{proof}
  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.  Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{V}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.  Thus this section of the Gramann necklace of $V$ looks like
  \begin{equation}\label{eq necklace}
  I_{n-3}^{V} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{V} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{V} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{V} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{V}
  \end{equation}
  where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.  Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.

  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.  $n-5$ is in $I_1^{V}$ as are at least one and at most two other elements.  If there is one such element call it $a$.  If there are two call them $a$ and $b$ with $a>b$.  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.  Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.

  \begin{figure}
    \includegraphics{messy}
    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.  The blue lines are the non-intersecting paths.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure}

  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.  This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.

  Now we know that $I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{W}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{V}$ to $\{n-2, n-1, n\}$.  This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}

  \begin{figure}
     \includegraphics{messyD}
    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
  \end{figure}

@@

  Now consider $I_{n-3}^{V}$.  By \eqref{eq necklace} $I_{n-3}^{V}$ contributes the same plusses as $I_{n_2}^{V}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.  Also, we have $n-3\in I_{n-3}^{V}$ be the location of $q$ and so $I_{k}^{W} = I_k^{V}\cup\{n-2\}$.  Thus the paths for $I^{W}_{n-3}$ are the same as for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.  This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.

  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.

  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.  By the algorithm, it would have to come when $n-5 \not\in I_j^{V}$.  By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{V}$, $I_{n-3}^{V}$, or $I_{n-2}^{V}$. The analysis above shows it does not come from $I_{n-3}^{V}$ or $I_{n-2}^{V}$.   Now, $n-4\in I_{n-4}^{V}$ by the location of $q$ and so $I_{n-4}^{V}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.

@@

\begin{lem}\label{lem other k}
  Let $V$ and $W$ be as in Lemma~\ref{lem I} and take $1<k<n-2$.  Suppose that if $n-2\in I_{n-2}^{V}$ then also $n-1\in I_{n-2}^{V}$.
  Then $I_k^{W}$ gives the same plusses as $I_{k}^{V}$ except that if there is a plus in the $n-3$ column for $I_{k}^{V}$ then this plus is shifted into the $n-2$ column and no plus was already in that location.
\end{lem}

\begin{proof}
  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.  Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.

  If $n-3\in I_{k}^{V}$ then by Lemma~\ref{lem I} $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.  If $n-2$ supports no propagators in $V$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $V$.  If $n-2$ supports at least one propagator in $V$ then by hypothesis so is $n-1$ and so we satisfy the hypotheses of Lemma~\ref{lem n-2 bad}.  Thus the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and this particular plus is not contributed to the Le diagram of $D$ by $I_{n-2}^{W}$.

  {}From $I_{k}^{V}$ there is a path from some vertical edge to the bottom edge $n-3$.  In $I_{k}^{W}$, $n-3$ is a vertical edge with no path and instead there must be a path to $n-2$.  By the previous paragraph no other path can end in $n-2$, so shifting the path that did go to $n-3$ to go to $n-2$ while leaving the others the same maintains non-crossingness and so must be the paths for $I_{k}^{W}$.  Thus the plus in the $n-3$ column for $C$ is shifted into the $n-2$ column, where there was no plus before, and no other plusses are changed.
\end{proof}
